Hydra Battles and Cie

### 2021-02-19 doc/chapter-primrec.tex
new exercise on Pr functions
correction of typos

>>>>

\index{primrec}{Exercises}
\begin{exercise}
Prove the following lemmas (which may help to solve thenext  exercise).

\begin{Coqsrc}
Lemma boundedSearch3 (P: naryRel 2) (b  : nat), 
    boundedSearch P b <= b.

Lemma boundedSearch4 (P: naryRel 2) (b  : nat):
  P b b = true -> P b (boundedSearch P b) = true.
\end{Coqsrc}
\end{exercise}

\begin{exercise}
Prove that the function which returns the  integer square root of any natural number  is primitive recursive.

\emph{You may start this exercise with the file
\url{../exercises/primrec/isqrt.v}.}
